\chapter{Corpus generado a partir de Quepy}\label{ap-3}

En la primera tabla se listan las preguntas incluidas en los ejemplos de la aplicación de Quepy. Todas ellas concuerdan con los patrones definidos en la aplicación para su interpretación correcta. En la segunda tabla se incluyen las reformulaciones construidas manualmente en base a estos ejemplos para cada una de las clases. Ninguna de estas reformulaciones concuerda con algún patrón de la aplicación.

\begin{longtable}{l l}
Instancia & Clase \\
\hline
List movies with Hugh Laurie & actedon\\
Movies with Matt LeBlanc & actedon\\
In what movies did Jennifer Aniston appear? & actedon\\
Which movies did Mel Gibson starred? & actedon\\
Movies starring Winona Ryder & actedon\\
Who are the actors of Titanic? & actorsof\\
Who acted in Alien? & actorsof\\
Who starred in Depredator? & actorsof\\
Actors of Fight Club & actorsof\\
List albums of Pink Floyd & albumsofband\\
What albums did Pearl Jam record? & albumsofband\\
Albums by Metallica & albumsofband\\
What albums did The Beatles make? & albumsofband\\
When was Korn formed? & bandfoundation\\
Radiohead members & bandmembers\\
What are the members of Metallica? & bandmembers\\
Who were the members of pink floyd? & bandmembers\\
List books by George Orwell & booksbyauthor\\
Which books did Suzanne Collins wrote? & booksbyauthor\\
What is the capital of Bolivia? & capitalcityof\\
What is the cast of Friends? & castof\\
Who works in Breaking Bad? & castof\\
List actors of Seinfeld & castof\\
Who is the creator of Breaking Bad? & creatorof\\
Who are the creators of Friends? & creatorof\\
Who is the director of Big Fish? & directorof\\
Who directed Pocahontas? & directorof\\
How many episodes does Seinfeld have? & episodecount\\
Number of episodes of Seinfeld & episodecount\\
How old is Bob Dylan & howoldis\\
List movies & listmovies\\
List TV shows & listtvshows\\
How long is Pulp Fiction & movieduration\\
What is the duration of The Thin Red Line? & movieduration\\
When was gravity released? & moviereleasedate\\
Release date of the hobbit? & moviereleasedate\\
List movies directed by Quentin Tarantino. & moviesbydirector\\
Movies directed by Martin Scorsese & moviesbydirector\\
Which movies did Mel Gibson directed & moviesbydirector\\
What is the music genre of Gorillaz? & musicgenre\\
Music genre of Radiohead & musicgenre\\
What is the plot of Titanic & plotof\\
What was Sherk about? & plotof\\
What is the population of China? & populationof\\
How many people live in Australia? & populationof\\
List presidents of Argentina? & presidentsof\\
List shows with Hugh Laurie & showswith\\
In what shows does Jennifer Aniston appears? & showswith\\
Shows with Matt LeBlanc & showswith\\
What is the language of Liberia? & spokenlanguageof\\
What is the spoken language in Russia? & spokenlanguageof\\
What is a car? & whatis\\
What is Seinfield? & whatis\\
Where in the world is the Eiffel Tower? & whereis\\
Where is Bill Gates from? & whereisfrom\\
Who is Tom Cruise? & whois\\
Who wrote The Little Prince? & whowrote\\
Who is the author of A Game Of Thrones? & whowrote\\
\hline
%\end{tabular}
\caption{Instancias extraídas de los ejemplos de Quepy y sus clases.}
\end{longtable}

\begin{longtable}{l l}
Instancia & Clase \\
\hline
What movies did James Dean appear in? & actedon \\
What actors worked on the matrix? & actedon \\
Actors of Memoirs of a Geisha & actedon \\
Actors that worked in the movie Matrix? & actedon \\
List the actors that worked in Alice in Wonderland & actedon \\
List actors starring in the movie The Nightmare Before Christmas & actedon \\
What works did the Beatles do? & albumsofband \\
Which works did Linkin Park make? & albumsofband \\
Albums recorded by the Guns n' Roses & albumsofband \\
What are titles of albums featuring The Black Eyed Peas? & albumsofband \\
When was the Red Hot Chili Peppers founded? & bandfoundation \\
When was the Rolling Stones born? & bandfoundation \\
When did My Chemical Romance start to perform? & bandfoundation \\
In what year did the Sex Pistols start to make recitals? & bandfoundation \\
List books written by J. K. Rowling & booksbyauthor \\
List of works written by George R.R. Martin & booksbyauthor \\
List of books created by Agatha Christie & booksbyauthor \\
What are titles of books written by Dan Brown? & booksbyauthor \\
What is the capital city of the United Kingdom? & capitalcityof \\
What is the capital of the country Germany? & capitalcityof \\
Which are the actors of Grey's Anatomy & castof \\
List of actors of the show The Addams Family & castof \\
Which were the actors of the TV show Uggly Betty & castof \\
Who create Stargate Atlantis? & creatorof \\
Who create The Neverending Story? & creatorof \\
When is Angelina Jolie's birthday? & howoldis \\
What is the age of Katy Perry? & howoldis \\
In what year was Madonna born? & howoldis \\
In what date did Bryan Cranston born? & howoldis \\
When was George Clooney born? & howoldis \\
What movies there are? & listmovies \\
What TV shows are? & listtvshows \\
What TV shows have been made? & listtvshows \\
How many minutes long is the lord of the rings? & movieduration \\
When was Harry Potter the movie released? & moviereleasedate \\
Steven spielberg was the director of what movies? & moviesbydirector \\
What type of music does AC DC? & musicgenre \\
What type of songs does the Rolling Stones? & musicgenre \\
Plot of Frozen? & plotof \\
What is the hitchhiker's guide to the galaxy about? & plotof \\
How many people is in Paraguay? & populationof \\
How many people there is in the People's Republic of China? & populationof \\
Who are the presidents of Bolivia? & presidentsof \\
Who have been presidents of the Republic of Egypt? & presidentsof \\
Who have been presidents of the Arab Republic of Egypt? & presidentsof \\
Who are the past liders of Brazil? & presidentsof \\
On what TV show does Hammond regularly appear? & showswith \\
Shows where Matthew Perry worked in? & showswith \\
What is the main spoken language in Poland? & spokenlanguageof \\
What is the main language in th republic of Argentina? & spokenlanguageof \\
Definition of computer & whatis \\
Where is the Statue of Liberty & whereis \\
Where was Matt Damon born? & whereisfrom \\
Where did he grow up? & whereisfrom \\
Where did J. R. R. Tolkien born? & whereisfrom \\
Biography of Charles Dickens & whois \\
Who is the writer of The Lord of the Rings? & whowrote \\
\hline
%\end{tabular}
\caption{Reformulaciones construidas manualmente y sus clases.}
\end{longtable}
